---
title: "class2"
output: html_document
date: "2025-10-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Import plain text files in R

Make use of the *scan* function, to read the entire text into our codes, automatically detecting the data types.

```{r}
nile <- scan("/Users/priyashrinarendran/Desktop/Priya/R_studio/02 codes pack 2/nile.txt")
```
file.exists("/Users/priyashrinarendran/Desktop/Priya/R_studio/02 codes pack 2/nile.txt")

Check the data type in variable *nile*

```{r}
typeof(nile)
```
#Plot histogram

```{r}
hist(nile)
```

Read data from *nile.txt* store each data as "character" type 

```{r}
nile_char <- scan("/Users/priyashrinarendran/Desktop/Priya/R_studio/02 codes pack 2/nile.txt", what = character())
nile_char
```

Check the data type in *nile_char*
```{r}
typeof(nile_char)
```

Read in plain text data separated by *;* for each data, by specifying the value for arguement *sep*

```{r}
sunset_sem<-scan("/Users/priyashrinarendran/Desktop/Priya/R_studio/02 codes pack 2/sunset-salvo.txt", what=character(), sep=";")
sunset_sem
sunset <- scan("/Users/priyashrinarendran/Desktop/Priya/R_studio/02 codes pack 2/sunset-salvo.txt",
what=character())
sunset
```

## Reading text data of different format

reading data with different data types
skip the 1st line

```{r}
running_lst <- scan("/Users/priyashrinarendran/Desktop/PRIYA/R_studio/02 codes pack 2/running_dat.tsv", what =list("",1.0,1.0,1.0,1.0,1.0,1.0),sep="\t", skip=1)
running_lst
```

# Export plain text files in R 

Output *sunset* data with "&" as separator 
```{r}
cat(sunset, file="sunset-salvo-amp.txt", sep="&")
```

## Import Delimeter-sepaarated values files in R

Read in structured data files, into R program as a table (*data frames*), automatically detect the data types for each variable/field.

```{r}
running_tbl <-read.table("/Users/priyashrinarendran/Desktop/PRIYA/R_studio/02 codes pack 2/running_dat.tsv", header=TRUE, sep="\t")
running_tbl
```

Show the struture of the table/data frame, also to show the data types for each variables 

```{r}
str(running_tbl)
```

###reading csv files in R

Read csv files into R program as sata frame.
*read.csv* read comma separated values, with "." as decimal point
*read.csv2* read semicolon separated values, with "," as decimal point

```{r}
running_df <- read.csv("/Users/priyashrinarendran/Desktop/PRIYA/R_studio/02 codes pack 2/running_dat.csv")
running_df
```

##export data frames in R

export data frames / table to a delimeter -separated values file. 
example, use "%" as separator
```{r}
write.table(running_df, file = "running_star.txt", sep = "%", dec="*")
```
```{r}
readLines("/Users/priyashrinarendran/Desktop/PRIYA/R_studio/02 codes pack 2/running_dat.csv")
```

## import XML in R 

```{r}
install.packages("xml2")
library("xml2")
```

Read data from HML into R as a tree hierarchial structure 
```{r}
stats_people <- read_xml("/Users/priyashrinarendran/Desktop/PRIYA/R_studio/02 codes pack 2/statisticians.xml")
stats_people
```

## Read XML as table 

Read XML files into R, store it as a data frame/table 

```{r}
install.packages("XML")
library("XML")
```

```{r}
stats_people_df <- xmlToDataFrame("/Users/priyashrinarendran/Desktop/PRIYA/R_studio/02 codes pack 2/statisticians.xml")
```
## Export XML files in R 

```{r}
bayes_record <- xml_children(stats_people)[[4]]
xml_remove(bayes_record)
write_xml(stats_people, "/Users/priyashrinarendran/Desktop/PRIYA/R_studio/02 codes pack 2/statisticians_no_bayes.xml")
bayes_record
```



